Generalised Management Strategy Evaluation: modelling biodiversity and food security

### 2019-01-04 notebook/presentation/GMSE_presentation.Rmd
More, closer to conclusion

sim_run <- observeEvent(input$run, {
              sim$data <- gmse(time_max = 30, land_dim_1 = 100, land_dim_2 = 100, 
                            observe_type = 1, res_death_K = 4000, plotting = FALSE,
                            manager_budget = 2000, user_budget = 500, 
                            scaring = TRUE, land_ownership = TRUE,
                            tend_crops = TRUE, stakeholders = 7,
                            res_consume = 1, RESOURCE_ini = 600)
              showNotification("Simulation has finished")
})

@@

@@

## Social conflict & management

@@

@@

@@

## Social conflict & management

@@

Saro pictures

>>>>

sim_run <- observeEvent(input$run, {
              sim$data <- gmse(time_max = 30, land_dim_1 = 100, land_dim_2 = 100, 
                            observe_type = 1, res_death_K = 4000, plotting = FALSE,
                            manager_budget = 2000, user_budget = 500, 
                            scaring = TRUE, land_ownership = TRUE,
                            tend_crops = TRUE, stakeholders = 7,
                            res_consume = 1, RESOURCE_ini = 600,
                            fixed_mark = 100, fixed_recapt = 200)
              showNotification("Simulation has finished")
})

@@

```{r, eval = FALSE}
new_sim <- gmse_apply(res_mod      = custom_resource_model,
                      obs_mod      = custom_observation_model,
                      man_mod      = manager, # GMSE default
                      use_mod      = user,    # GMSE default
                      stakeholders = 5,       # GMSE option
                      custom_arg   = 200      # For custom function
                      );
```

The `gmse_apply` function [needs to be looped](https://confoobio.github.io/gmse/articles/SI2.html#running-gmse-simulations-by-looping-gmse_apply) for modelling more than one time step (e.g., using the `old_list` argument).

@@

## Social conflict and management {.smaller}

@@

**Investigate how disagreement over target population size affects natural resource management**

<br><br>

@@

- Model divergent goals expressed by conservationists and resource users (two stake-holders)
- Modified `gmse_apply` to allow for policy lobbying and illegal harvesting
- Varied manager 'impartiality' (susceptability to lobbying pressure) 
- Compared population dynamics given conservationist and resource user disagreement over population target
    - Manager ($N_{m}$)
    - Conservationist ($N_{c}$)
    - Resource user ($N_{u}$)

@@

## Social conflict and management

@@

## Behavioural games in conservation

![](gabon3.jpg)

## Behavioural games in conservation

![](madagascar.jpg)

## Behavioural games in conservation

![](goosebump.png)
